Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
webbox -> datapalette

Each task had an A and B condition.  The A condition, the participant could only use WebBox to make their decision; and in the B condition the participant was given the choice to using any websites they desired and or workbook in Microsoft Excel containing the data taken from the data sources to make their choice on individual spreadsheets.

Each study consisted of two tasks, one A and one B condition.  Each participant was given 10 minutes to complete a task.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute WebBox tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

@@

In the A condition, where participants used WebBox to complete their tasks they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of WebBox, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.

@@

In the exit survey, the users noted that they would use WebBox for finding a property to rent/buy, choosing a job and purchasing electronic devices, in the future.  However, one participant said that they would not use it for things like deciding on a restaurant because ``it would cheapen the experience'' by removing the spontaneity, but would use it for making more important decisions.  In order to improve our solutions the participants suggested making the origin of the information clearer, sorting instances, and explanations of ratings and scoring systems (however some of these are not transparent on websites).

@@

Two contrasting approaches that participants followed was to use the data to rule out candidates, or to use the data to
directly compare candidates at once. Our pool of participants exhibited both behaviours evenly, however in the condition
when using the WebBox interface, significantly more comparison (and visualisation of values) was performed, with fewer
participants using the ``ruling out'' process. A consequence of this was that when asked to justify their choices, users were
able to verify their values on-screen immediately, whereas those who had ruled-out had to memorise their reasons, with
mixed success  -- many participants had to look through the data sources to re-find the reasons why they has ruled out some choices.
Therefore, the uses that were using WebBox were more confident in their choices, and knew exactly why they had chosen them,
often pointing to the screens to show and verify each choice as they explained them.

>>>>

Each task had an A and B condition.  The A condition, the participant could only use DataPalette to make their decision; and in the B condition the participant was given the choice to using any websites they desired and or workbook in Microsoft Excel containing the data taken from the data sources to make their choice on individual spreadsheets.

Each study consisted of two tasks, one A and one B condition.  Each participant was given 10 minutes to complete a task.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

@@

In the A condition, where participants used DataPalette to complete their tasks they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of DataPalette, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.

@@

In the exit survey, the users noted that they would use DataPalette for finding a property to rent/buy, choosing a job and purchasing electronic devices, in the future.  However, one participant said that they would not use it for things like deciding on a restaurant because ``it would cheapen the experience'' by removing the spontaneity, but would use it for making more important decisions.  In order to improve our solutions the participants suggested making the origin of the information clearer, sorting instances, and explanations of ratings and scoring systems (however some of these are not transparent on websites).

@@

Two contrasting approaches that participants followed was to use the data to rule out candidates, or to use the data to
directly compare candidates at once. Our pool of participants exhibited both behaviours evenly, however in the condition
when using the DataPalette interface, significantly more comparison (and visualisation of values) was performed, with fewer
participants using the ``ruling out'' process. A consequence of this was that when asked to justify their choices, users were
able to verify their values on-screen immediately, whereas those who had ruled-out had to memorise their reasons, with
mixed success  -- many participants had to look through the data sources to re-find the reasons why they has ruled out some choices.
Therefore, the uses that were using DataPalette were more confident in their choices, and knew exactly why they had chosen them,
often pointing to the screens to show and verify each choice as they explained them.
